Conservation of interaction partners between related plants varies widely across communities and between plant families.

### 2019-02-15 manuscript/phylogenetic_signal_manuscript.tex
realised I need to update the by-family regressions still

  This permutation approach also allows us to estimate type I and type II 
  error for our analysis. To do this, we created 500 permutations of each 
  permuted network and, again keeping the observed phylogenetic distances 
  between plant species, repeated our analyses. We can then determine the 
  number of permuted networks which appear to have significant 
  overlap-phylogenetic distance relationships relative to the permutations 
  of these permuted networks (type I error). [[How does this get at type II error?]]

@@

  Next, we examined the connection between our network-level observations
  and the plant families present in each community.
  Specifically, we tested the hypothesis that
  varying relationships between phylogenetic distance and
  pairwise niche overlap are due to the different distributions 
  of families across networks. To do this, we performed a non-parametric
  permutational multi-variate analysis of variance
  (PERMANOVA;~\citealp{Anderson2001}) using the change in log
  odds of two plants sharing an interaction partner to 
  predict the Bray-Curtis dissimilarity of networks
  based on the composition of their plant component
  (defined as the proportions of the plant community
  made up by each plant family present in the entire dataset).
  We used Bray-Curtis dissimilarity because, for a given
  pair of networks, only those plant families that appear
  in at least one network are considered~\citep{Anderson2001,Cirtwill2015}; 
  that is, the absence of rare plant families will not make 
  two networks appear more similar than they actually are.

@@

>>>>

  This permutation approach also allows us to estimate type I and type II 
  error for our analysis. To do this, we created 500 permutations of each 
  permuted network and, again keeping the observed phylogenetic distances 
  between plant species, repeated our analyses. We can then determine the 
  number of permuted networks which appear to have significant 
  overlap-phylogenetic distance relationships relative to the permutations 
  of these permuted networks (type I error). Type II error can be determined
  from the distribution of p-values obtained when comparing the permuted 
  networks to permutations of the permuted networks. The distribution of 
  p-values should be uniform. [[I still do not see how this gives us the
  probability of a false negative... ]] [[Something to do with comparing
  the distributions of p-values from glmer and the ones from the randomization.
  I don't think I actually kept the p-values from glmer, but the p-values from
  the randomizations are bang-on uniform.]]
  [[Maybe go back to whichever reviewer comment this was based on?]]
  [[How does this get at type II error?]] 
  [[Seems we can calculate power for a specific alternative hypothesis by
  comparing distributions of p-values from glmer and from the permutations.
  I can only pray I kept the p-values from the randomised regressions...]]

@@

  Next, we examined the connection between our network-level observations
  and the plant families present in each community.
  Specifically, we tested the hypothesis that
  varying relationships between phylogenetic distance and
  pairwise niche overlap are due to the different distributions 
  of families across networks. We defined the relationship between
  phylogenetic distance and niche overlap as the change in 
  log odds of two plants in a given network sharing an interaction 
  partner per million years of divergence (i.e., the slope from the 
  regression of niche overlap against phylogenetic distance within
  a single network). We then related differences in this relationship
  to differences in the composition of the plant community in each
  network using a non-parametric permutational multi-variate 
  analysis of variance (PERMANOVA;~\citealp{Anderson2001}).
  As we did not wish to inflate the perceived similarity between
  pairs of networks which did not include many of the same families,
  we used Bray-Curtis dissimilarity to define differences in plant
  community composition. Bray-Curtwis dissimilarity considers only
  those plant families which appear in at least one of a pair of
  networks~\citep{Anderson2001,Cirtwill2015}, ensuring that the
  shared absence of rare plant families will not make 
  two networks appear more similar than they actually are.

@@

  [[I need to double-check that I'm actually doing this, and that the right things
  are being plotted.]][[I think I may not have updated this since the family composition 
  was not singificant. Still of interest, so redo. Guess I will also need to do randomisations
  to make the p-vals here?]]
